### 2020-01-26 experiments.tex
Updates from Overleaf

For Java and Python, we did not have to worry about invalidating tool improvements by basing our results on benchmark code.  We therefore aimed to use realistic, important source code.  We selected top GitHub projects (defined by number of stars) for each language, and removed projects with fewer than 5 developers or less than six months of commit history (as well as projects that did not build).  For Java, we analyzed the top 15 projects satisfying our criteria, with a maximum of 623,355 LOC and a minimum of 3,957 LOC, and a total size of 1.8 million LOC.  Because the Universal Mutator does not ``know'' Java syntax, and Java is very verbose, the Java compiler rejected a large number of the generated mutants (e.g., deleting declarations), leaving just over 70,000 mutants, ranging from 136 to 10,016 per project.

@@

For {\bf RQ4} there were no clean projects for the known-to-be-aggressive Pylint.  Performance for the other two tools was worse on projects for which they were clean, again failing to support the possibility that our definition of killing a mutant under-reports detection for non-clean code.

>>>>

For Java and Python, we did not have to worry about invalidating tool improvements by basing our results on benchmark code.  We therefore aimed to use realistic, important source code.  We selected top GitHub projects (defined by number of stars) for each language, and removed projects with fewer than 5 developers or less than six months of commit history (as well as projects that did not build).  For Java, we analyzed the top 15 projects satisfying our criteria, with a maximum of 623,355 LOC and a minimum of 3,957 LOC, and a total size of 1.8 million LOC.  Because the Universal Mutator does not ``know'' Java syntax, and Java is very verbose, the Java compiler rejected a large number of the generated mutants (e.g., deleting declarations).  We still, due to the huge size of the source files and thus number of mutants (and time to compile full projects), restricted our analysis to files where Universal Mutator's implementation of TCE \cite{TCE} for Java was useful, i.e. files that could be compiled and the bytecode compared without processing the full project, leaving us with just over 70,000 mutants, ranging from 136 to 10,016 per project.

@@

For {\bf RQ4} there were no clean projects for the known-to-be-aggressive Pylint.  Performance for the other two tools was worse on projects for which they were clean, again failing to support the possibility that our definition of killing a mutant is too restrictive.
